Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Apply consistency regarding how to format Python's doctest
Add missing comma

\begin{itemize}
\item Add markup syntax for interactive examples to Haddock
\item Add markup syntax for properties to Haddock
\item
    Implement a tool, similar to Python's Doctest, that can verify
    examples and test properties in Haddock comments.
    The implementation is discussed in Section~\ref{sec:doctest}.

@@

GHCi's type defaulting~\cite{ghc-manual} applies to properties.  If a default type is
not suitable explicit type-signatures can be used:

>>>>

\begin{itemize}
\item Add markup syntax for interactive examples to Haddock
\item Add markup syntax for properties to Haddock
\item
    Implement a tool, similar to Python's {\tt doctest} module, that
    can verify examples and test properties in Haddock comments.
    The implementation is discussed in Section~\ref{sec:doctest}.

@@

GHCi's type defaulting~\cite{ghc-manual} applies to properties.  If a default type is
not suitable, explicit type-signatures can be used:
